Multisensor Architecture for an Intersection Management System

### 2018-02-28 ch3-arch_sys.tex
Started processing blocks section and some little fixes

In the designing of an IMS, there are four main stages that have to be performed from the data source to final output: preprocessing, feature analysis, pattern recognition and situation assessment. The aim of the first stage is to extract data of interest from the raw sensor information, using filtering to remove noise and irrelevant data, and background subtraction techniques to get the foreground of the scene. Spatial-temporal alignment of data is also performed in this stage. In the second stage, the objective is to identify elements within the foreground and extract relevant features of them. The third stage receives the set of features from the previous stage and performs recognition and classification tasks. Also, tracking and prediction of objects' state is performed based on historic information. In the fourth stage, object behaviour and inter-objects interaction are analysed to identify context and detect situations or events of interest. This output could be delivered to an optional fifth stage of decision and control, to a human operator, or to a traffic agent or institution, to take immediate actions on traffic control, issue traffic tickets, warn drivers about possible incidents or improve transportation policies in a long-term basis. In figure \ref{proc_stages}, previously described stages are depicted, including common task performed at each of these stage and also is shown how the data volume is reduced while data meaning increases in the last stages.

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.55]{fig/3/processing_stages_and_tasks.png}
\caption{Dataflow through processing stages in an IMS an commonly performed tasks}
\label{proc_stages}
\end{figure}

@@

For publishers and subscribers to exchange messages, channels are defined with labels using a namespace approach that describe the source of data and the kind of data. For example a channel containing raw data from a laser scanner could be labeled as "/sensors/range/laser\_N/data/raw".

@@

The data model proposed for the system includes the abstraction of the sensing elements, the intersection model and the data used and generated by the processing blocks. For the sensing elements, a Sensor base class and two derived classes, RangeSensor class and ImageSensor class, are defined.

@@

The sensors sets are composed of zero or more sensor objects, as defined previously. An Area class is defined as having a bounding box and a label	. From this class, a derived class Leg is defined for containing additional information about the legs of the intersection, such as heading of the leg, approaching or departure type. In figure \ref{data_model} is shown an UML diagram for the aforementioned classes and their relationships

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.55]{fig/3/data_model.pdf}
\caption{UML diagram of defined entities and their relationships}
\label{data_model}
\end{figure}

The purpose of all the labels attributes within each class is to serve as an identifier of the channel in which the entity is publishing or subscribing to.

--Describe data from flow

@@

>>>>

In the designing of an IMS, there are four main stages that have to be performed from the data source to final output: preprocessing, feature analysis, pattern recognition and situation assessment. The aim of the first stage is to extract data of interest from the raw sensor information, using filtering to remove noise and irrelevant data, and background subtraction techniques to get the foreground of the scene. Spatial-temporal alignment of data is also performed in this stage. In the second stage, the objective is to identify elements within the foreground and extract relevant features of them. The third stage receives the set of features from the previous stage and performs recognition and classification tasks. Also, tracking and prediction of objects' state is performed based on historic information. In the fourth stage, object behaviour and inter-objects interaction are analysed to identify context and detect situations or events of interest. This output could be delivered to an optional fifth stage of decision and control, to a human operator, or to a traffic agent or institution, to take immediate actions on traffic control, issue traffic tickets, warn drivers about possible incidents or improve transportation policies in a long-term basis. In figure \ref{proc_stages}, previously described stages are depicted, including a list of common tasks performed at each of these stages and also it is shown how the data volume is reduced while data meaning increases in the last stages.

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.55]{fig/3/processing_stages_and_tasks.png}
\caption{Processing stages in an IMS and commonly performed tasks within each of them}
\label{proc_stages}
\end{figure}

@@

For publishers and subscribers to exchange messages, channels are defined with labels using a namespace approach that describe the source of data and the kind of data. For example a channel containing raw data from a laser scanner could be labeled as \texttt{/sensors/range/laser\_1/data/raw}.

@@

The data model proposed for the system includes the abstraction of the sensing elements and the intersection model. For the sensing elements, a Sensor base class and two derived classes, RangeSensor class and ImageSensor class, are defined.

@@

The sensors sets are composed of zero or more sensor objects, as defined previously. An Area class is defined as having a bounding box and a label	. From this class, a derived class, Leg, is defined for containing additional information about the legs of the intersection, such as heading of the leg, approaching or departure type. In figure \ref{data_model} is shown an UML diagram for the aforementioned classes and their relationships

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.5]{fig/3/data_model.pdf}
\caption{UML diagram of defined entities and their relationships}
\label{data_model}
\end{figure}

The purpose of all the labels attributes within each class is to serve as an identifier of the channel in which the entity is publishing or subscribing to; in other words, to identify where is data generated from or where is data going to. For example, channel \texttt{/sensors/range/laser\_1/data/raw} contains raw data from a laser scanner labeled as \texttt{"laser\_1"}. Or channel \texttt{/legs/leg\_3/occupancy/} refers to the occupancy level of the leg labeled as \texttt{"leg\_3"}.

@@

As stated in previous section, there are defined four stages in the processing flow, namely, preprocessing, feature analysis, pattern recognition and situation assessment. Within each of these stages there are different methods and techniques used to process the data and it is possible that those methods are suitable to perform fusion between homogeneous or heterogeneous data.

Below are detailed different processing blocks implemented as part of the whole architecture proposal, classified by the stage of processing in which are located in the process flow. Also, it is shown the format of data input, data output and parameters needed for configuration and execution.

\subsubsection{Preprocessing}
\subsubsection{Feature Analysis}
\subsubsection{Pattern Recognition}
\subsubsection{Situation Assesment}
\subsubsection{Tools and Utilities}
